Are kelp forests different? A comparison of kelp forests between contrasting

### 2018-07-25 paper_draft.Rmd
edits

library(tidyverse)
library(vegan)
library(ggplot2)
library(reshape2)
library(ggpubr)

@@

flora_df <- read.csv(file = "data/flora.csv", check.names = FALSE)
fauna_df <- read.csv(file = "data/fauna.csv", check.names = FALSE)
benthic <- read.csv(file = "data/benthic.csv", check.names = FALSE)
cover_df <- read.csv(file = "data/cover.csv", check.names = FALSE)
kelp_df <- read.csv(file = "data/kelp.csv", check.names = FALSE)

@@

```{r diversity fauna script, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap='Comparison of raw biomass species data between sites. Graph A represents flora and graph B represents fauna.'}

@@

plot_fauna <- ggplot(data = fauna_lng, aes(x = species, y= biomass, fill = site)) + 
              geom_bar(stat = "identity", show.legend = TRUE                                      ,position=position_dodge(),
              size=.3) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'white', colour =                      'white')) +
              ylab("") + 
              xlab("") +
              coord_flip()

ggarrange(plot_flora, plot_fauna, ncol = 2, nrow = 1, labels = "AUTO", legend = "bottom", common.legend = TRUE, align = "none", heights = c(1.5,1))

@@

flora_mds <-  read.csv(file = "data/flora.csv", row.names = 'id', sep = ",", header = TRUE) 
site  <- flora_mds$site
flora_mds <- subset(flora_mds,select=-c(site))

flora_log <- decostand(flora_mds, method='log') # Log-transform data, accounts for possible over-estimate of species with a large biomass but low abundance
dist1<-vegdist(flora_log, method='bray')
nmds1 <- metaMDSiter(dist1,k=2)

nmds1_plot <- plot(nmds1, type = "p")

fauna_mds <-  read.csv(file = "data/fauna.csv", row.names = 'id', sep = ",", header = TRUE) 
site  <- fauna_mds$site
fauna_mds <- subset(fauna_mds,select=-c(site))
fauna_mds <- fauna_mds[which(rowSums(fauna_mds) > 0),]

fauna_log <- decostand(fauna_mds, method='range', na.rm = TRUE) # Log-transform data, accounts for possible over-estimate of species with a large biomass but low abundance
dist2<-vegdist(fauna_mds, method='bray')
nmds2 <- metaMDS(dist2, k = 3)

nmds2_plot <- plot(nmds2, type = "p")

>>>>

library(tidyverse)
library(vegan)
library(ggplot2)
library(reshape2)
library(vegan)
library(gridExtra)
library(lubridate)
library(GGally)
library(ggpubr)
```

@@

benthic <- read.csv(file = "data/benthic.csv", check.names = FALSE)
cover_df <- read.csv(file = "data/cover.csv", check.names = FALSE)
kelp_df <- read.csv(file = "data/kelp.csv", check.names = FALSE)

@@

```{r message=FALSE, warning=FALSE}

flora_df <- read.csv(file = "data/flora.csv", check.names = FALSE)
fauna_df <- read.csv(file = "data/fauna.csv", check.names = FALSE)

@@

plot_fauna <- ggplot(data = fauna_lng, aes(x = species, y= biomass, fill = site)) + 
              geom_bar(stat = "identity", show.legend = TRUE                                      ,position=position_dodge(),
              size=.3) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'white', colour =                      'white')) +
              ylab("") + 
              xlab("") +
              coord_flip()
```

```{r, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap='Comparison of raw biomass species data between sites. Graph A represents flora and graph B represents fauna.'}

ggarrange(plot_flora, plot_fauna, ncol = 2, nrow = 1, labels = "AUTO", legend = "bottom", common.legend = TRUE, align = "none", heights = c(1.5,1))
```

@@

## Temperature

## Wave parameters
